CommonMind Consortium: DLPFC

### 2020-09-18 combined_analysis/diff.networks.Rmd
Update diff networks

>>>>

# NULL network

# Sex network
## Difference networks
```{r diff.networks.null}

resVersion = "Sex"

METADATA$rnd = sample(c('A','B'), nrow(METADATA), replace=TRUE)
METADATA$rnd = factor(METADATA$rnd, c('A','B'))

variable = 'rnd'

```{r testing.null}
# Hypothesis testing         
df_test = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors, METADATA, useSLED=FALSE)   #, BPPARAM=SnowParam(18)) 
```

```{r null.results}
p = df_test$P.Value[df_test$Cohort=="MSSM-Penn-Pitt"]
print(1 - qvalue(p)$pi0)
hist(p)

p = df_test$P.Value[df_test$Cohort== "NIMH-HBCC"]
1 - qvalue(p)$pi0
hist(p)
```
